Transportation network with multiple lines

### 2022-04-05 multiple_lines/notes/latex/Notes_trajet.tex
Updated mutlilines notes

A flow on edges is represented by the $(n \times n)$ \emph{flow matrix} $\mathbf{X} = (x_{ij})$, verifying
\begin{align}
x_{ij} &\geq 0, \qquad \forall i,j, \\
a_{ij} = 0 &\Rightarrow x_{ij} = 0, \qquad \forall i,j, \\ 
x_{i\bullet} + \sigma^\text{in}_i &= x_{\bullet i} + \sigma^\text{out}_i, \qquad \forall i.
\end{align}
Again, we can decompose the flow matrix with 
\begin{equation}
\mathbf{X} = \mathbf{X}_\text{W} + \mathbf{X}_\text{B} \qquad \mathbf{X}_\text{W} := \sum_{k=1}^l \mathbf{X}_k
\end{equation}
where $\mathbf{X}_k$ represent the flow inside line $k$, $\mathbf{X}_\text{W}$ is the flow inside all lines, and $\mathbf{X}_\text{B}$ the flow between lines. This decomposition allows us to define 
the \emph{vector of flow entering lines} $\bm{\rho}_\text{in} = (\rho^\text{in}_i)$ and the \emph{vector of flow leaving lines} $\bm{\rho}_\text{out} = (\rho^\text{out}_i)$, with
\begin{align}
\bm{\rho}_\text{in} &:= \bm{\sigma}_\text{in} + \mathbf{X}^\top_\text{B} \mathbf{e}_n, \\
\bm{\rho}_\text{out} &:= \bm{\sigma}_\text{out} + \mathbf{X}_\text{B} \mathbf{e}_n,
\end{align}
where $\mathbf{e}_n$ is the vector of ones of size $n$. It is easy to see that we still have $\rho^\text{in}_\bullet = \rho^\text{out}_\bullet$. \\

@@

Let $\mathcal{P}_{st}$ be the set of \emph{admissible} shortest-paths between $s$ and $t$ on $\mathcal{G}$. We can denote by $\text{P}_{st}(i, j)$ the probability of having edge $(i, j) \in \wp$ when drawing a path $\wp$ from $\mathcal{P}_{st}$. We have 
\begin{equation}
\text{P}_{st}(i, j) := \frac{1}{|\mathcal{P}_{st}|}\sum_{\wp \in \mathcal{P}_{st}} \delta((i, j) \in \wp),
\end{equation}
where $\delta(.)$ designate the indicator function. If we are given an origin-destination matrix $\mathbf{N} = (n_{st})$, we can compute the \emph{shortest-path flow matrix}, noted $\mathbf{X}_\text{sp} = (x^\text{sp}_{ij})$, with:
\begin{equation}
x^\text{sp}_{ij} = \sum_{st} \text{P}_{st}(i, j) n_{st} \label{sp_comp}
\end{equation}
This matrix contains the flow on each edge if we suppose that the flow follows shortest-paths.

>>>>

A flow on edges is represented by the $(n \times n)$ \emph{flow matrix} $\mathbf{X} = (x_{ij})$, verifying
\begin{align}
x_{ij} &\geq 0, \qquad \forall i,j, \\
a_{ij} = 0 &\Rightarrow x_{ij} = 0, \qquad \forall i,j, \\ 
x_{i\bullet} + \sigma^\text{out}_i &= x_{\bullet i} + \sigma^\text{in}_i, \qquad \forall i.
\end{align}
Again, we can decompose the flow matrix with 
\begin{equation}
\mathbf{X} = \mathbf{X}_\text{W} + \mathbf{X}_\text{B} \qquad \mathbf{X}_\text{W} := \sum_{k=1}^l \mathbf{X}_k
\end{equation}
where $\mathbf{X}_k$ represent the flow inside line $k$, $\mathbf{X}_\text{W}$ is the flow inside all lines, and $\mathbf{X}_\text{B}$ the flow between lines. This decomposition allows us to define 
the \emph{vector of flow entering lines} $\bm{\rho}_\text{in} = (\rho^\text{in}_i)$ and the \emph{vector of flow leaving lines} $\bm{\rho}_\text{out} = (\rho^\text{out}_i)$, with
\begin{align}
\bm{\rho}_\text{in} &:= \bm{\sigma}_\text{in} + \mathbf{X}^\top_\text{B} \mathbf{e}_n, \\
\bm{\rho}_\text{out} &:= \bm{\sigma}_\text{out} + \mathbf{X}_\text{B} \mathbf{e}_n,
\end{align}
where $\mathbf{e}_n$ is the vector of ones of size $n$. It is easy to see that we still have $\rho^\text{in}_\bullet = \rho^\text{out}_\bullet$. \\

@@

Let $\mathcal{P}_{st}$ be the set of \emph{admissible} shortest-paths between $s$ and $t$ on $\mathcal{G}$. We can denote by $\text{P}_{st}(i, j)$ the probability of having edge $(i, j) \in \wp$ when drawing a path $\wp$ from $\mathcal{P}_{st}$. We have 
\begin{equation}
\text{P}_{st}(i, j) := \frac{1}{|\mathcal{P}_{st}|}\sum_{\wp \in \mathcal{P}_{st}} \delta((i, j) \in \wp),
\end{equation}
where $\delta(.)$ designate the indicator function. If we are given an origin-destination matrix $\mathbf{N} = (n_{st})$, we can compute the \emph{shortest-path flow matrix}, noted $\mathbf{X}_\text{sp} = (x^\text{sp}_{ij})$, with:
\begin{equation}
x^\text{sp}_{ij} = \sum_{st} \text{P}_{st}(i, j) n_{st} \label{sp_comp}
\end{equation}
This matrix contains the flow on each edge if we suppose that the flow follows shortest-paths. \\

We can rewrite equation (\ref{sp_comp}) by defining the $(n^2 \times n^2)$ \emph{shortest-path - edge matrix} $\mathbf{S} = (s_{\alpha \beta})$ with
\begin{equation}
s_{\alpha \beta} = \begin{cases}
\text{P}_{st}(i, j) & \text{if } \alpha = s + n(t - 1) \text{ and }  \beta = i + n(j - 1), \\
0 & \text{otherwise}.
\end{cases}
\end{equation}
Then (\ref{sp_comp}) writes
\begin{equation}
\
\end{equation}
